Finite-time Analysis of Frequentist Strategies for Multi-armed Bandits

### 2018-01-08 Appendix/AppendixConc.tex
Latest on 24/11/2017
Latest on 8/1/2017

\subsection{Sample space}

\subsection{Events}

\subsection{Sigma-algebra}

\subsubsection{Borel-sigma algebra}

\subsection{Measure}

\subsubsection{The probability measure}

\subsection{The triplet}

\subsection{Filtration}

\section{Martingale}

\subsection{Super-martingale}

\subsection{Sub-martingale}

\section{Convergence theorems}

\subsection{Monotone convergence theorem}

\subsection{Dominated convergence theorem}

\subsection{Fatou's Lemma}

@@

In this section we state some of the concentration inequalities used in the proofs in several chapters of the thesis. Concentration inequality deals with the control of the tail of the average of independent random variables from their expected mean.

@@

\subsection{Chernoff-Hoeffding Bound}

@@

\begin{align*}
&\Pb\lbrace S_n - n\E[S_n] \geq \epsilon \rbrace \leq \exp\left( -\dfrac{2\epsilon^2}{n \sum_{i=1}^n(a_i -b_i)}\right) \\
%%%%%%%%%%%%%%%%%%%%%%
&=\Pb\lbrace S_n - n\E[S_n] \leq - \epsilon \rbrace \leq \exp\left( -\dfrac{2\epsilon^2}{n \sum_{i=1}^n(a_i -b_i)}\right)
\end{align*}

Considering all the random variables bounded in $[0,1]$, the above two inequalities can be reduced to,

\begin{align*}
&\Pb\lbrace \left|\dfrac{S_n}{n} - \E[S_n]\right| \geq \epsilon \rbrace \leq 2\exp\left( - 2\epsilon^2 n \right) \\
%%%%%%%%%%%%%%%%%%%%%%
&=\Pb\lbrace \left|\hat{r} - r\right| \geq \epsilon \rbrace \leq 2\exp\left( - 2\epsilon^2 n \right)
\end{align*}

\subsection{Empirical Bernstein inequality}

@@

Considering all the random variables bounded in $[0,1]$, the above two inequalities can be reduced to,

\begin{align*}
&\Pb\lbrace \left|\dfrac{S_n}{n} - \E[S_n]\right| \geq \epsilon \rbrace \leq 2\exp\left( -\dfrac{2\epsilon^2 n}{\left(2\sigma^2 + \frac{2\epsilon}{3}\right)}\right) \\
%%%%%%%%%%%%%%%%%%%%%%
&=\Pb\lbrace \left|\hat{r} - r\right| \geq \epsilon \rbrace \leq 2\exp\left( -\dfrac{2\epsilon^2 n}{\left(2\sigma^2 + \frac{2\epsilon}{3}\right)}\right)
\end{align*}

>>>>

%\subsection{Sample space}
%
%
%
%\subsection{Events}
%
%
%
%\subsection{Sigma-algebra}
%
%
%
%\subsubsection{Borel-sigma algebra}
%
%
%
%\subsection{Measure}
%
%
%
%\subsubsection{The probability measure}
%
%
%
%\subsection{The triplet}
%
%
%
%\subsection{Filtration}
%
%
%
%\section{Martingale}
%
%
%
%\subsection{Super-martingale}
%
%
%
%\subsection{Sub-martingale}
%
%
%\section{Convergence theorems}
%
%
%\subsection{Monotone convergence theorem}
%
%
%
%\subsection{Dominated convergence theorem}
%
%
%
%\subsection{Fatou's Lemma}

@@

In this section we state some of the concentration inequalities used in the proofs in several chapters of the thesis. Concentration inequality deals with the control of the deviation of the average of independent random variables from their expected mean.

@@

The Markov;s inequality gives us a very loose bound which is further tightened by the Chernoff-Hoeffding Bound and Bernstein Inequality.

\subsection{Chernoff-Hoeffding Bound}
\label{app:chernoff}

@@

\begin{align*}
&\Pb\lbrace S_n - n\E[S_n] \geq \epsilon \rbrace \leq \exp\left( -\dfrac{2\epsilon^2}{n \sum_{i=1}^n(a_i -b_i)}\right) \\
%%%%%%%%%%%%%%%%%%%%%%
&\Pb\lbrace S_n - n\E[S_n] \leq - \epsilon \rbrace \leq \exp\left( -\dfrac{2\epsilon^2}{n \sum_{i=1}^n(a_i -b_i)}\right)
\end{align*}

Considering all the random variables bounded in $[0,1]$, then both the right and left tail inequality can be reduced to,

\begin{align*}
&\Pb\left\lbrace \left|\dfrac{S_n}{n} - \E[S_n]\right| \geq \epsilon \right\rbrace \leq 2\exp\left( - 2\epsilon^2 n \right) \\
%%%%%%%%%%%%%%%%%%%%%%
%&= 2\exp\left( - 2\epsilon^2 n \right)
\end{align*}

Hence, we obtain that, 
\begin{align*}
\Pb\lbrace \left|\hat{r} - r\right| \geq \epsilon \rbrace \leq 2\exp\left( - 2\epsilon^2 n \right)
\end{align*}

\subsection{Empirical Bernstein inequality}
\label{app:bernstein}

@@

Considering all the random variables bounded in $[0,1]$, then both the right and left tail inequality can be reduced to,

\begin{align*}
&\Pb\left\lbrace \left|\dfrac{S_n}{n} - \E[S_n]\right| \geq \epsilon \right\rbrace \leq 2\exp\left( -\dfrac{2\epsilon^2 n}{\left(2\sigma^2 + \frac{2\epsilon}{3}\right)}\right) \\
%%%%%%%%%%%%%%%%%%%%%%
%&=\Pb\lbrace \left|\hat{r} - r\right| \geq \epsilon \rbrace \leq 2\exp\left( -\dfrac{2\epsilon^2 n}{\left(2\sigma^2 + \frac{2\epsilon}{3}\right)}\right)
\end{align*}

Hence, we obtain that,

\begin{align*}
\Pb\lbrace \left|\hat{r} - r\right| \geq \epsilon \rbrace \leq 2\exp\left( -\dfrac{2\epsilon^2 n}{\left(2\sigma^2 + \frac{2\epsilon}{3}\right)}\right)
\end{align*}
